Growth and inequality in public good provision --- an extended replication

### 2022-11-04 analysis/quarto/paper.qmd
work on paper and template.

@@

@@

In the terminology of @Hamermesh2007, I ran both a _pure_ as well as a _scientific replication_ of one treatment of GMTV's dynamic public good game. The pure replication re-analyzes the original data. [Appendix A](#A:-Pure-Replication) documents [errors I identified]() in the original paper. The scientific replication, where I utilize a different sample drawn from a different population in a different situation, is described in the following sections.

@@

As in the NOPUNISH 10 Period treatment of GMTV, I ran sessions with groups of four ($i \in I=\{1,2,3,4\}$), an initial endowment of $N_i^1 = 20$ tokens, $T=10$ periods, a private account with a return of $1$ and a group account with a return of $1.5$ ($\Rightarrow$ MPCR$\equiv \frac{1.5}{4}$), such that:

@@

@@

The experiment's source code be found on [GitHub](https://github.com/Howquez/coopUncertainty).^[https://github.com/Howquez/coopUncertainty]

@@

Participants entered the experiment at appointed times remotely from home. They first saw a welcome screen. After agreeing to the privacy policy, they could proceed to the instructions individually. Having read these instructions, each participant has also seen a demo-screen explaining the user interface. Before proceeding, they had to answer six comprehension questions correctly. Subsequently, they saw a waiting screen until they could be matched with three other participants, who have answered the comprehension questions correctly. Once matched, they were exposed to the decision screen over ten periods. At the end of the last period, participants saw results of all periods. Subsequently, they were exposed to a voluntary climate action, where they could donate (some of) their earnings to offset carbon dioxide. Subsequently, I elicited risk preferences [@HoltLaury2002] and finished with GMTV's questionnaire.

@@

@@

The analyses in this section were pre-registered [@preregistration]. I also pre-registered a RMarkdown file with the exact code I intended to use [here](https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd).^[https://github.com/Howquez/coopUncertainty/tree/July21Replication/analysis/reports/rmd to run the code, you need to executed the .Rmd files in this repository in the order that is indicated by its file names.] Even though I had to adjust a few lines of code, the main findings in the following section can also be replicated using the pre-registered code.

>>>>

```{r constants}
SHOW_UP_FEE <- 5
EXCHANGE_RATE <- 1/20
```

@@

```{r earnings}

# This chunk requires raw data
files <- list.files(path = "../../data/replication/",
                       recursive = TRUE,
                       full.names = TRUE)
csvs <- list()

for(i in files){
  name <- str_extract(string = i,
                      pattern = "2021.*")

full <- rbindlist(l = csvs,
                  use.names = TRUE) %>%
  data.table()

# subset data of participants who have completed the study
tmp <- full[participant._index_in_pages >= 76 & 
              participant.time_started != "" & 
              !(is.na(dPGG.1.player.contribution)) &
              participant.label != ""]

# calculate total payoff
tmp[, finalPayoff := (dPGG.10.player.stock - dPGG.10.player.donation + HLPL.1.player.payoff) * EXCHANGE_RATE + SHOW_UP_FEE]

earningsMean <- tmp[, mean(finalPayoff, na.rm = TRUE)]
earningsSD   <- tmp[, sd(finalPayoff, na.rm = TRUE)]
```

@@

In the terminology of @Hamermesh2007, I ran both a _pure_ as well as a _scientific replication_^[@Parsons2022 use the term of a _conceptual replication_ which means the same.] of one treatment of GMTV's dynamic public good game. The pure replication re-analyzes the original data. [Appendix A](#A:-Pure-Replication) documents [errors I identified]() in the original paper. The scientific replication, where I utilize a different sample drawn from a different population in a different situation, is described in the following sections.

@@

As in the NOPUNISH 10 Period treatment of GMTV, I ran sessions with groups of four ($i \in I=\{1,2,3,4\}$), an initial endowment of $N_i^1 = 20$ tokens^[A token was worth `r EXCHANGE_RATE` Euros.], $T=10$ periods, a private account with a return of $1$ and a group account with a return of $1.5$ ($\Rightarrow$ MPCR$\equiv \frac{1.5}{4}$), such that:

@@

## Voluntary Climate Action (VCA)

Like GMTV we employ a real giving task after the abstract game. In contrast to GMTV and like @GKLS2020, we employed a VCA, where they could donate (some of) their earnings to offset carbon dioxide (that is, by retiring emission permits from the EU ETS).^[Importantly, @GKLS2020 made the VCA decision with a fresh endowment _before_ they played the abstract game. I deviate from their procedure to match GMTV's procedure.]
To ensure that each participant had the same basic level of information about the impact of their decision, I provided some basic information about the mechanism. The information also highlighted that the mitigation came into operation on a European level.
Finally, I informed the participants that the documentation of individual and aggregate contributions were posted immediately after the experiments online. To avoid privacy or social image concerns, participants learned their unique and random IDs, which they needed to identify their individual contributions.
This document certified that their contributions have been used to offset [1.82 tons](https://www.compensators.org/compensatelist/?searchterm=stefan+traub) of carbon dioxide emissions.

@@

@@

Participants entered the experiment at appointed times remotely from home. They first saw a welcome screen. After agreeing to the privacy policy, they could proceed to the instructions individually. Having read these instructions, each participant has also seen a demo-screen explaining the user interface. Before proceeding, they had to answer six comprehension questions correctly. Subsequently, they saw a waiting screen until they could be matched with three other participants, who have answered the comprehension questions correctly. Once matched, they were exposed to the decision screen over ten periods. At the end of the last period, participants saw results of all periods. Subsequently, they made their VCA decision, before I elicited risk preferences [@HoltLaury2002] and finished with GMTV's questionnaire.

@@

```{r totalTimeSpent}
tmp <- duration[page_index == 1 | page_index == 76, 
                .(page_index, participant_code, page_submission)]
tmp[order(participant_code, page_index), 
    total := page_submission - data.table::shift(x = page_submission,
                                                 n = 1,
                                                 type = "lag"),
    by = participant_code]

total_completion_time <- tmp[!is.na(total), mean(total/ 60) %>% round()]
```

The experiment lasted around `r total_completion_time` minutes on average. The earnings of the average subject were `r earningsMean %>% round(digits = 2)` Euros (sd = `r earningsSD  %>% round(digits = 2)`).^[This values include earnings from the incentivized risk elicitation task that are not part of the analysis.]

## Pre-registration {#sec-registration}

Parts of the analyses are pre-registered [@preregistration]. In addition, I pre-registered the exact analyses I planned to run when I designed designed the experiment on [GitHub](https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd).^[https://github.com/Howquez/coopUncertainty/tree/July21Replication/analysis/reports/rmd to run the code, you need to executed the .Rmd files in this repository in the order that is indicated by its file names.]. GitHub is a website and cloud-based service where developers---and researchers alike---can store and manage their code. The service is based on Git^[Git is a specific open-source version control system developed in 2005.] and designed for version control. Importantly, changes are timestamped and can be tracked. Moreover, one can create branches, that is, duplicates of code -- either to work collaborative or to archive a certain state. Accordingly, I archived my analyses scripts and created a [branch](https://github.com/Howquez/coopUncertainty/tree/July21Replication) a few days _before_ we collected data.

The analysis that makes the most sense now that you have collected the data is a little different, though: Because the more representative subject pool was exhausted earlier than expected, I recruited students unwantedly and changed parts of the scripts.^[The source code of this document contains the analysis and can be found [here](https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd): https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd] Because the originally planned analysis code is archived and reproducible, these changes are transparent.

@@

### 2022-11-04 analysis/quarto/paper.tex
work on paper and template.

\begin{keyword}
    Replication study \sep Non-convenience sample \sep Open
science \sep Dynamic public good game \sep Online experiment \sep 
    Generalizability
\end{keyword}
\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, sharp corners, frame hidden, boxrule=0pt, breakable, enhanced, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi

@@

In the terminology of \citet{Hamermesh2007}, I ran both a \emph{pure} as
well as a \emph{scientific replication} of one treatment of GMTV's
dynamic public good game. The pure replication re-analyzes the original
data. \protect\hyperlink{A:-Pure-Replication}{Appendix A} documents
\href{}{errors I identified} in the original paper. The scientific
replication, where I utilize a different sample drawn from a different
population in a different situation, is described in the following
sections.

@@

As in the NOPUNISH 10 Period treatment of GMTV, I ran sessions with
groups of four (\(i \in I=\{1,2,3,4\}\)), an initial endowment of
\(N_i^1 = 20\) tokens, \(T=10\) periods, a private account with a return
of \(1\) and a group account with a return of \(1.5\) (\(\Rightarrow\)
MPCR\(\equiv \frac{1.5}{4}\)), such that:

@@

@@

The experiment's source code be found on
\href{https://github.com/Howquez/coopUncertainty}{GitHub}.\footnote{https://github.com/Howquez/coopUncertainty}

@@

Participants entered the experiment at appointed times remotely from
home. They first saw a welcome screen. After agreeing to the privacy
policy, they could proceed to the instructions individually. Having read
these instructions, each participant has also seen a demo-screen
explaining the user interface. Before proceeding, they had to answer six
comprehension questions correctly. Subsequently, they saw a waiting
screen until they could be matched with three other participants, who
have answered the comprehension questions correctly. Once matched, they
were exposed to the decision screen over ten periods. At the end of the
last period, participants saw results of all periods. Subsequently, they
were exposed to a voluntary climate action, where they could donate
(some of) their earnings to offset carbon dioxide. Subsequently, I
elicited risk preferences \citep{HoltLaury2002} and finished with GMTV's
questionnaire.

@@

@@

The analyses in this section were pre-registered
\citep{preregistration}. I also pre-registered a RMarkdown file with the
exact code I intended to use
\href{https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd}{here}.\footnote{https://github.com/Howquez/coopUncertainty/tree/July21Replication/analysis/reports/rmd
  to run the code, you need to executed the .Rmd files in this
  repository in the order that is indicated by its file names.} Even
though I had to adjust a few lines of code, the main findings in the
following section can also be replicated using the pre-registered code.

>>>>

\begin{keyword}
    Replication study \sep Non-convenience sample \sep Open
science \sep Dynamic public good game \sep Online experiment \sep 
    Generalizability
\end{keyword}
\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, frame hidden, sharp corners, enhanced, breakable, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi

@@

In the terminology of \citet{Hamermesh2007}, I ran both a \emph{pure} as
well as a \emph{scientific replication}\footnote{\citet{Parsons2022} use
  the term of a \emph{conceptual replication} which means the same.} of
one treatment of GMTV's dynamic public good game. The pure replication
re-analyzes the original data.
\protect\hyperlink{A:-Pure-Replication}{Appendix A} documents
\href{}{errors I identified} in the original paper. The scientific
replication, where I utilize a different sample drawn from a different
population in a different situation, is described in the following
sections.

@@

As in the NOPUNISH 10 Period treatment of GMTV, I ran sessions with
groups of four (\(i \in I=\{1,2,3,4\}\)), an initial endowment of
\(N_i^1 = 20\) tokens\footnote{A token was worth 0.05 Euros.}, \(T=10\)
periods, a private account with a return of \(1\) and a group account
with a return of \(1.5\) (\(\Rightarrow\) MPCR\(\equiv \frac{1.5}{4}\)),
such that:

@@

\hypertarget{voluntary-climate-action-vca}{%
\subsection{Voluntary Climate Action
(VCA)}\label{voluntary-climate-action-vca}}

Like GMTV we employ a real giving task after the abstract game. In
contrast to GMTV and like \citet{GKLS2020}, we employed a VCA, where
they could donate (some of) their earnings to offset carbon dioxide
(that is, by retiring emission permits from the EU ETS).\footnote{Importantly,
  \citet{GKLS2020} made the VCA decision with a fresh endowment
  \emph{before} they played the abstract game. I deviate from their
  procedure to match GMTV's procedure.} To ensure that each participant
had the same basic level of information about the impact of their
decision, I provided some basic information about the mechanism. The
information also highlighted that the mitigation came into operation on
a European level. Finally, I informed the participants that the
documentation of individual and aggregate contributions were posted
immediately after the experiments online. To avoid privacy or social
image concerns, participants learned their unique and random IDs, which
they needed to identify their individual contributions. This document
certified that their contributions have been used to offset
\href{https://www.compensators.org/compensatelist/?searchterm=stefan+traub}{1.82
tons} of carbon dioxide emissions.

@@

@@

Participants entered the experiment at appointed times remotely from
home. They first saw a welcome screen. After agreeing to the privacy
policy, they could proceed to the instructions individually. Having read
these instructions, each participant has also seen a demo-screen
explaining the user interface. Before proceeding, they had to answer six
comprehension questions correctly. Subsequently, they saw a waiting
screen until they could be matched with three other participants, who
have answered the comprehension questions correctly. Once matched, they
were exposed to the decision screen over ten periods. At the end of the
last period, participants saw results of all periods. Subsequently, they
made their VCA decision, before I elicited risk preferences
\citep{HoltLaury2002} and finished with GMTV's questionnaire.

@@

The experiment lasted around 25 minutes on average. The earnings of the
average subject were 11.23 Euros (sd = 4.85).\footnote{This values
  include earnings from the incentivized risk elicitation task that are
  not part of the analysis.}

\hypertarget{sec-registration}{%
\subsection{Pre-registration}\label{sec-registration}}

Parts of the analyses are pre-registered \citep{preregistration}. In
addition, I pre-registered the exact analyses I planned to run when I
designed designed the experiment on
\href{https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd}{GitHub}.\footnote{https://github.com/Howquez/coopUncertainty/tree/July21Replication/analysis/reports/rmd
  to run the code, you need to executed the .Rmd files in this
  repository in the order that is indicated by its file names.}. GitHub
is a website and cloud-based service where developers---and researchers
alike---can store and manage their code. The service is based on
Git\footnote{Git is a specific open-source version control system
  developed in 2005.} and designed for version control. Importantly,
changes are timestamped and can be tracked. Moreover, one can create
branches, that is, duplicates of code -- either to work collaborative or
to archive a certain state. Accordingly, I archived my analyses scripts
and created a
\href{https://github.com/Howquez/coopUncertainty/tree/July21Replication}{branch}
a few days \emph{before} we collected data.

The analysis that makes the most sense now that you have collected the
data is a little different, though: Because the more representative
subject pool was exhausted earlier than expected, I recruited students
unwantedly and changed parts of the scripts.\footnote{The source code of
  this document contains the analysis and can be found
  \href{https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd}{here}:
  https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd}
Because the originally planned analysis code is archived and
reproducible, these changes are transparent.

@@
